-

### 2023-02-01 DRAFT_homogeneous_impact_areas.Rmd
bug: Big cache

```{r, echo=FALSE}
Sys.Date()
```

@@

```{r, warning=F}
infra_agg_discrete_vect <- eaTools::ea_homogeneous_area(infra_agg_discrete, groups = infrastructureIndex)
```

@@

```{r test-2, fig.cap="A vectorized version of the Infrastructure indeks over Trondheim on a four-step discrete scale."}
tm_shape(infra_agg_discrete_vect_trd)+
  tm_polygons(col="infrastructureIndex",
              style = "cat")+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="white")
```

As can be seen in the figure above, `st_warp` merges grid cells that have the same value, and the vectorized raster doesn't not end up being that big in the end.

## Chech national distribution

@@

```{r, echo=F}
# silently read cached file
infra_stats <- readRDS("P:/41201785_okologisk_tilstand_2022_2023/data/cache/infra_stats.rds")
```

>>>>

@@

```{r , eval=F}
infra_agg_discrete_vect <- 
  eaTools::ea_homogeneous_area(infra_agg_discrete, 
                                groups = infrastructureIndex)
path <- ifelse(dir == "C:", 
        "P:/41201785_okologisk_tilstand_2022_2023/data/cache/",
        "/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/cache/")

saveRDS(infra_agg_discrete_vect, paste0(path, "infra_agg_discrete_vect.rds"))
```

```{r, include=F}
infra_agg_discrete_vect <- readRDS(paste0(path, "infra_agg_discrete_vect.rds"))
```

@@

```{r test-2, fig.cap="A vectorized version of the Infrastructure index over Trondheim on a four-step discrete scale."}
tm_shape(infra_agg_discrete_vect_trd)+
  tm_polygons(col="infrastructureIndex",
              style = "cat")+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="white")
```

As can be seen in the figure above, `st_warp` merges grid cells that have the same value, and the vectorized raster doesn't end up being that big in the end.

## Check national distribution

@@

```{r, echo=F}
# silently read cached file
path <- ifelse(dir == "C:", 
        "P:/41201785_okologisk_tilstand_2022_2023/data/cache/infra_stats.rds",
        "/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/cache/infra_stats.rds")
infra_stats <- readRDS(path)
```
